%-------------------------
% Resume in Latex
% Author : Yosvany Blanco Otaño
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\nocite{*}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Yosvany Blanco Otaño} \\ \vspace{1pt}
    \small (214)--650--4603 $|$ \href{mailto:yosvany@yosvanyblanco.com}{\underline{yosvany@yosvanyblanco.com}} $|$ 
    \href{https://linkedin.com/in/yosvanyblanco}{\underline{linkedin.com/in/yosvanyblanco/}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart{}

    \resumeSubheading{Amazon}{June 2019 --- Present}{Software Development Engineer II | Privacy}{Austin, TX}
      \resumeItemListStart{}
        \resumeItem{Designed and implemented microservice using Java and Amazon Coral service framework for storing and retrieving privacy related data used by internal privacy audit service.}
        \resumeItem{Major contributor to first iteration of internal privacy audit service using Python, Cloudformation, AWS Lambda, and AWS S3 which has cataloged over 25,000 services and has over 51,000 unique internal customers.}  
        \resumeItem{Designed and implemented CSV import/export feature using Go, Typescript, React, S3, Lambda, SNS, SQS, and Postgres which has allowed 8500+ customers to bulk insert and edit data in privacy tool.}
        \resumeItem{Major contributor in migration of privacy audit service to a Go backend running on AWS Fargate from AWS Lambda and Python which led to roughly 66\% reduction in request latency.}
        \resumeItem{Designed and implemented async process to ingest privacy (DSAR and deletion) data in realtime from sister services using SNS, SQS, Lambda, and Java.}
        \resumeItem{Implemented AWS Lambda interceptor using Node.js and Typescript which verified users visiting our website were authenticated simplifying our service authentication flow and improving security.}
        \resumeItem{Created CDK pattern which generates multiple AWS Lambdas and APIGateway from Smithy and OpenAPI allowing developers on the team to focus on writing business logic.}
        \resumeItem{Enhanced our product’s reach to all development teams within Amazon by integrating with internal service review tool which is utilized for auditing production readiness.}
        \resumeItem{Researched and advocated for switch to internal service framework which helped reduce creation of base level production ready services from 1 month to under 2 weeks.}
        \resumeItem{Created reusable infrastructure patterns using CDK for AWS Lambda, S3, SNS, SQS, and internal pipeline to reduce team development time.}
        \resumeItem{Introduced reusable patterns in frontend React Cypress tests allowing developers to focus on testing their features.}
        \resumeItem{Improved the reliability of our software by implementing integration testing infrastructure using internal tool Amazon Hydra.}
        \resumeItem{Have owned many features end to end (backend, frontend, design, testing, support, etc..)}
        \resumeItem{Extensive experience with oncall, customer issue triage, runbook entries, data migrations, etc..}
        \resumeItem{Conducted 70+ interviews to identify and hire top software engineering talent.}
      \resumeItemListEnd{}
      
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 - Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading{General Motors}{June 2017 --- June 2019}{Software Developer | Manufacturing}{Austin, TX}
      \resumeItemListStart{}
        \resumeItem{Designed and Implemented file validation system for internal audit tool using Java and Spring Boot with a presentation layer in Angular 2.}
        \resumeItem{Added authentication and authorization to Spring Boot service using JWT and internal identity service.}
        \resumeItem{Created reusable S3 client in Java reducing undifferentiated effort for the team.}
        \resumeItem{Added caching layer to Spring Boot service using Redis which reduced homepage load times by 80\%}
        \resumeItem{Designed and implemented proof of concept clustered message filtering system using C\#, Akka.Net and Akka.Net Cluster library for routing and surfacing plant floor robot issues.}
        \resumeItem{Added SonarQube code scanners to development pipeline improving code quality.}
        \resumeItem{Increased unit test coverage on legacy Java service to above 80\% with meaningful tests.}
        \resumeItem{Migrated a legacy internal website to Spring boot and Angular from Spring and Java Server Pages.}
        \resumeItem{Created repeatable patterns for automated frontend tests using internal testing library leveraging Selenium.}
    \resumeItemListEnd{}

  \resumeSubHeadingListEnd{}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AWS}{: Lambda, S3, Fargate, DynamoDB, RDS, SNS, SQS, IAM, EventBridge, CDK, Cloudformation} \\
     \textbf{Languages}{: Go, Java, Python, Typescript, Smithy} \\
     \textbf{Frameworks/Libraries}{: React, Angular, JUnit, Spring Boot} \\
     \textbf{Developer Tools}{: Git, Intellij, VSCode, Postman} \\
     \textbf{Databases}{: Postgres, DynamoDB}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart{}
    \resumeSubheading{University of North Texas}{Denton, TX}{Bachelor of Science in Computer Science}{May 2017}
  \resumeSubHeadingListEnd{}


%-------------------------------------------
\end{document}
